Equations & R Code

### 2017-01-02 manuscript/coexistence-stability_ms.tex
moves refs before figs
updates k typo
updates fig3 legend typo

\noindent where \(D(\tau_k)\), \(N(\tau_k)\), and \(R(\tau_k)\) are the
abundances of each state at the end of growing season \emph{k} and
\(\tau_k^+\) denotes the beginning of growing season \(k\). The
activation of dormant biomass to live biomass is controlled by
\(\gamma\), which is year (\emph{k}) and species (\emph{i}) specific.
Dormant biomass is equal to a constant fraction (\(\alpha\)) of live
biomass at the end of the previous season (\(N_{i}(\tau_k)\)), plus
survival (\(1-\eta_i\)) of dormant biomass (\(D_{i}(\tau_k)\)) at the
end of the previous year and dormant biomass remaining after live
biomass activation (\(D_{i}(\tau_k)(1-\gamma_{i,\tau_k})\)). Live
biomass is equal to newly activated dormant biomass
(\(\gamma_{i,t}D_{i}(\tau_k)\)), minus some fraction of live biomass
that is converted to dormant biomass (\((1-\alpha_i)N_{i}(\tau_k)\)) We
assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource
pool (\emph{R}) at the start of the growing season \emph{k}+1 is
\(R(\tau_k^+) = R^+\), where \(R^+\) is a random resource pulse drawn
from a log-normal distribution with mean \(\mu(R^+)\) and standard
deviation \(\sigma(R^+)\). Model parameters and notation are described
in Table 1.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=2.5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure3.png}
  \caption{The effect of environmental variability on ecosystem variability when species coexist via relative nonlinearity. (A) The species pool increases from one to four species, with the fourth species being most unstable (e.g., resource conservative to resource acquisitive). Increasing environmental variability (the SD of annual resource availability) allows for greater species richness, but species additions do not modulate the effect of environmental variability on ecosystem variability. (B) The species pool increases from one to four species, with the fourth species being most stable (e.g., resource acquisitive to resrouce conservative). In this case, increasing environmental variability allows for greater realized species richness and can temper the effect of environmental variability. In (B), there is limited parameter space under which only three species coexist, which is why a three species community is missing. Parameter values are as in Figure 1C.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[height=4in]{./components/coexistence_stability_infographic_v2.png}
  \caption{Example of how species additions under increasing environmental variability can buffer ecosystem stability when species coexist via the storage effect. Environmental variability ($\sigma^2_E$) increases linearly with time on the \emph{x}-axis. (A) Time series of species' biomass (colored lines) in a closed community where colonization of new species is prevented and (B) its associated coefficient of variation (Rolling CV; calculated over 100-yr moving window) through time. (C) Time series of species' biomass in an open community where colonization by new species from the regional pool of four species becomes possible as environmental variation increases. The trajectory of total biomass CV in the open community (D) asymptotes at lower variability than in the closed community (B) due to the buffering effect of species richness. Parameter values are as in Figure 2A except for $\alpha$s: (A-C) $\alpha_1 = 0.5, \alpha_2 = 0.494, \alpha_3 = 0.49, \alpha_4 = 0.483$.}
\end{figure}

@@

>>>>

\noindent where \(D(\tau_k)\), \(N(\tau_k)\), and \(R(\tau_k)\) are the
abundances of each state at the end of growing season \emph{k} and
\(\tau_k^+\) denotes the beginning of growing season \(k+1\). The
activation of dormant biomass to live biomass is controlled by
\(\gamma\), which is year (\emph{k}) and species (\emph{i}) specific.
Dormant biomass is equal to a constant fraction (\(\alpha\)) of live
biomass at the end of the previous season (\(N_{i}(\tau_k)\)), plus
survival (\(1-\eta_i\)) of dormant biomass (\(D_{i}(\tau_k)\)) at the
end of the previous year and dormant biomass remaining after live
biomass activation (\(D_{i}(\tau_k)(1-\gamma_{i,\tau_k})\)). Live
biomass is equal to newly activated dormant biomass
(\(\gamma_{i,t}D_{i}(\tau_k)\)), minus some fraction of live biomass
that is converted to dormant biomass (\((1-\alpha_i)N_{i}(\tau_k)\)) We
assume the resource pool is not replenished within a growing season.
Resource replenishment occurs between growing seasons, and the resource
pool (\emph{R}) at the start of the growing season \emph{k}+1 is
\(R(\tau_k^+) = R^+\), where \(R^+\) is a random resource pulse drawn
from a log-normal distribution with mean \(\mu(R^+)\) and standard
deviation \(\sigma(R^+)\). Model parameters and notation are described
in Table 1.

@@

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=2.5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure3.png}
  \caption{The effect of environmental variability on ecosystem variability when species coexist via relative nonlinearity. (A) The species pool increases from one to four species, with the fourth species being most unstable (e.g., resource conservative to resource acquisitive). Increasing environmental variability (the SD of annual resource availability) allows for greater species richness, but species additions do not modulate the effect of environmental variability on ecosystem variability. (B) The species pool increases from one to four species, with the fourth species being most stable (e.g., resource acquisitive to resrouce conservative). In this case, increasing environmental variability allows for greater realized species richness and can temper the effect of environmental variability. In (B), there is limited parameter space under which only three species coexist, which is why a three species community is missing. Parameter values are as in Figure 2C.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[height=4in]{./components/coexistence_stability_infographic_v2.png}
  \caption{Example of how species additions under increasing environmental variability can buffer ecosystem stability when species coexist via the storage effect. Environmental variability ($\sigma^2_E$) increases linearly with time on the \emph{x}-axis. (A) Time series of species' biomass (colored lines) in a closed community where colonization of new species is prevented and (B) its associated coefficient of variation (Rolling CV; calculated over 100-yr moving window) through time. (C) Time series of species' biomass in an open community where colonization by new species from the regional pool of four species becomes possible as environmental variation increases. The trajectory of total biomass CV in the open community (D) asymptotes at lower variability than in the closed community (B) due to the buffering effect of species richness. Parameter values are as in Figure 2A except for $\alpha$s: $\alpha_1 = 0.5, \alpha_2 = 0.494, \alpha_3 = 0.49, \alpha_4 = 0.483$.}
\end{figure}
